Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012

### 2018-07-03 paper/ijm.tex
Update ijm.tex
Referee 1 page 2,3 small changes

We find that in case of, Estonian language is associated with very
small albeit slowly increasing wage premium over
the years, but only for women.
Russian skills, on the other hand, are clearly related to
higher wage but the relationship is slowly fading. English fluency was
associated with a very large wage premium during the first decade
after the introduction of the market economy, it's importance later
declined, but was still large in 2012.  For
women, the wage premium of each of these languages is roughly equal.
In contrast, the sole language that plays a role in determining
unemployment is Estonian, it's fluency is associated with
approximately 5 percentage points lower unemployment rate.
These results suggest that Estonian labour market is
segmented both along gender and the ethnic boundaries, men
more likely occupied in less communication-intense jobs.
This view is
supported by data from a specifically designed ethnic integration
dataset.

@@

According to the report of the Ministry of Education and Research the number
of students, whose mother tongue is not Estonian in basic schools who study in the Estonian language increased from 17,5\% in 2005 to 25,8\% in 2015 due to the growing popularity of immersion
classes (enrolment of classes rose from 7,8\% in 2005 to 17,5\% in 2015).
At the same time the number of students whose mother tongue is not Estonian studying in Estonian basic schools slowly dropped respectively from 9,5\% to  8,3\% \citep{HTM2015}.

>>>>

We find that in case of, Estonian language is associated with very
small albeit slowly increasing wage premium over
the years, but only for women.
Russian skills, on the other hand, are clearly related to
higher wage but the relationship is slowly fading. English fluency was
associated with a very large wage premium during the first decade
after the introduction of the market economy, it's importance later
declined, but was still large in 2012.  For
women, the wage premium of each of these languages is roughly equal.
In contrast, the sole language that plays a role in determining
unemployment is Estonian, it's fluency is associated with
approximately 5 percentage points lower probability of being unemployed.
These results suggest that Estonian labour market is
segmented both along gender and the ethnic boundaries, men
more likely occupied in less communication-intense jobs.
This view is
supported by data from a specifically designed ethnic integration
dataset.

@@

According to the report of the Ministry of Education and Research the number
of students, whose mother tongue is not Estonian in basic schools who study in the Estonian language increased from 17.5\% in 2005 to 25.8\% in 2015 due to the growing popularity of immersion
classes (enrolment of classes rose from 7.8\% in 2005 to 17.5\% in 2015).
At the same time the number of students whose mother tongue is not Estonian studying in Estonian basic schools slowly dropped respectively from 9.5\% to  8.3\% \citep{HTM2015}.
